---
title: "Safety Data Analysis"
format: 
  html:
    self-contained: true
    embed-resources: true
    code-fold: true
    code-summary: "Show code"
---

```{r}
#| label: load-packages
#| include: false

library(dplyr)
library(ggplot2)
library(readxl)

figure_output_dir <- "figures"
dir.create(figure_output_dir, showWarnings = FALSE)

save_plot <- function(plot, filename, width = 10, height = 6) {
  ggsave(
    file.path(figure_output_dir, paste0(filename, ".png")),
    plot = plot,
    width = width,
    height = height,
    dpi = 600,
    bg = "white"
  )
  ggsave(
    file.path(figure_output_dir, paste0(filename, ".pdf")),
    plot = plot,
    width = width,
    height = height,
    device = "pdf",
    bg = "white"
  )
}

event_type_grays <- c(
  "Visit Observation" = "gray20",
  "Parent/Guardian Interview" = "gray70",
  "Clinician Interview" = "white"
)

site_grays <- c(
  "Site 1" = "gray20",
  "Site 2" = "gray50",
  "Site 3" = "gray80"
)
```

## Data Import

```{r}
#| label: load-data

# Load the Excel data
safety_data <- read_excel("data/Safety II Unique Codes 8-27-2025.xlsx")

# Display basic information about the data
glimpse(safety_data)
```

## Data Overview

```{r}
#| label: data-summary

# Display first few rows
head(safety_data)

# Basic summary statistics
summary(safety_data)

# Dataset dimensions
data_dims <- tibble::tibble(
  Metric = c("Number of observations", "Number of variables"),
  Value = c(nrow(safety_data), ncol(safety_data))
)

knitr::kable(data_dims)
```

## Section 1: Basic Descriptive Statistics

### Overall Study Statistics

```{r}
#| label: overall-stats

# Total number of patients
total_patients <- safety_data %>%
  distinct(patient_id) %>%
  nrow()

# Total number of unique resilient behaviors (events)
total_events <- safety_data %>%
  distinct(event_id) %>%
  nrow()

# Create summary table
overall_summary <- tibble::tibble(
  Metric = c("Total patients included", "Total unique resilient behaviors"),
  Count = c(total_patients, total_events)
)

knitr::kable(overall_summary,
             caption = "Overall Study Statistics")
```

### Statistics by Site

```{r}
#| label: site-stats

site_summary <- safety_data %>%
  group_by(site_id) %>%
  summarise(
    n_patients = n_distinct(patient_id),
    n_events = n_distinct(event_id)
  ) %>%
  arrange(site_id)

# Display as table
knitr::kable(site_summary, 
             col.names = c("Site ID", "Number of Patients", "Number of Resilient Behaviors"),
             caption = "Summary Statistics by Site")
```

### Statistics by Type of Resilient Behavior (Safety II Code)

```{r}
#| label: safety-code-stats

safety_code_summary <- safety_data %>%
  group_by(safety2_code) %>%
  summarise(
    n_events = n_distinct(event_id)
  ) %>%
  arrange(desc(n_events))

# Display as table
knitr::kable(safety_code_summary,
             col.names = c("Safety II Code", "Number of Resilient Behaviors"),
             caption = "Summary Statistics by Safety II Code")
```

### Statistics by Event Type

```{r}
#| label: event-type-stats

event_type_summary <- safety_data %>%
  group_by(event_type) %>%
  summarise(
    n_events = n_distinct(event_id)
  ) %>%
  arrange(desc(n_events))

# Display as table
knitr::kable(event_type_summary,
             col.names = c("Event Type", "Number of Resilient Behaviors"),
             caption = "Summary Statistics by Event Type")
```

### Summary Visualizations

```{r}
#| label: summary-plots
#| fig-width: 10
#| fig-height: 8

# Plot 1: Distribution by Site
p1 <- ggplot(site_summary, aes(x = factor(site_id), y = n_events)) +
  geom_bar(stat = "identity", fill = "gray35") +
  labs(title = "Resilient Behaviors by Site",
       x = "Site ID",
       y = "Number of Unique Resilient Behaviors") +
  theme_minimal()

# Plot 2: Top 10 Safety II Codes
top_safety_codes <- safety_code_summary %>%
  slice_head(n = 10)

p2 <- ggplot(top_safety_codes, aes(x = reorder(safety2_code, n_events), y = n_events)) +
  geom_bar(stat = "identity", fill = "gray35") +
  coord_flip() +
  labs(title = "Top 10 Safety II Codes by Frequency",
       x = "Safety II Code",
       y = "Number of Unique Resilient Behaviors") +
  theme_minimal()

# Plot 3: Distribution by Event Type
p3 <- ggplot(event_type_summary, aes(x = reorder(event_type, n_events), y = n_events)) +
  geom_bar(stat = "identity", fill = "gray35") +
  coord_flip() +
  labs(title = "Resilient Behaviors by Event Type",
       x = "Event Type",
       y = "Number of Unique Resilient Behaviors") +
  theme_minimal()

# Display and save plots
save_plot(p1, "summary-site-distribution", width = 10, height = 6)
save_plot(p2, "summary-top-safety-codes", width = 10, height = 6)
save_plot(p3, "summary-event-type-distribution", width = 10, height = 6)
p1
p2
p3
```

## Section 2: Mean Unique Resilient Behaviors by Type and Event Source

### Data Preparation and Analysis

```{r}
#| label: prepare-mean-data

# Create mappings for labels
resilient_type_labels <- c(
  "ant" = "Anticipation",
  "mon" = "Monitoring", 
  "resp" = "Response",
  "learn" = "Learning"
)

event_type_labels <- c(
  "obs" = "Visit Observation",
  "par" = "Parent/Guardian Interview",
  "prov" = "Clinician Interview"
)

# Extract resilient behavior type from safety2_code (first part before underscore)
safety_data_processed <- safety_data %>%
  mutate(
    resilient_type = sub("_.*$", "", safety2_code),
    resilient_type_label = resilient_type_labels[resilient_type],
    event_type_label = event_type_labels[event_type]
  ) %>%
  filter(resilient_type %in% names(resilient_type_labels),
         event_type %in% names(event_type_labels))

# First, get all unique patients
all_patients <- unique(safety_data_processed$patient_id)

# Create all possible combinations
all_combinations <- expand.grid(
  patient_id = all_patients,
  resilient_type = names(resilient_type_labels),
  event_type = names(event_type_labels),
  stringsAsFactors = FALSE
) %>%
  mutate(
    resilient_type_label = resilient_type_labels[resilient_type],
    event_type_label = event_type_labels[event_type]
  )

# Calculate behaviors per patient-combination
behaviors_per_patient <- safety_data_processed %>%
  group_by(patient_id, resilient_type, event_type) %>%
  summarise(
    n_unique_behaviors = n_distinct(event_id),
    .groups = "drop"
  )

# Join with all combinations to ensure zeros for missing combinations
patient_behaviors_complete <- all_combinations %>%
  left_join(behaviors_per_patient, 
            by = c("patient_id", "resilient_type", "event_type")) %>%
  mutate(n_unique_behaviors = coalesce(n_unique_behaviors, 0L))

# Calculate mean unique behaviors per patient for each combination
mean_behaviors <- patient_behaviors_complete %>%
  group_by(resilient_type, resilient_type_label, event_type, event_type_label) %>%
  summarise(
    mean_behaviors = mean(n_unique_behaviors),
    sd_behaviors = sd(n_unique_behaviors),
    n = n(),
    se = sd_behaviors / sqrt(n),
    ci_lower = mean_behaviors - 1.96 * se,
    ci_upper = mean_behaviors + 1.96 * se,
    .groups = "drop"
  )

# Display summary table
knitr::kable(
  mean_behaviors %>%
    select(resilient_type_label, event_type_label, mean_behaviors, ci_lower, ci_upper, n) %>%
    rename(
      "Resilient Behavior Type" = resilient_type_label,
      "Event Type" = event_type_label,
      "Mean Behaviors per Patient" = mean_behaviors,
      "95% CI Lower" = ci_lower,
      "95% CI Upper" = ci_upper,
      "N" = n
    ),
  digits = 3,
  caption = "Mean Unique Resilient Behaviors per Patient by Type and Event Source"
)
```

### Grouped Bar Charts

#### Version 1: Without Error Bars

```{r}
#| label: mean-behaviors-plot-no-error
#| fig-width: 10
#| fig-height: 6

# Set factor levels for proper ordering
mean_behaviors$resilient_type_label <- factor(
  mean_behaviors$resilient_type_label,
  levels = c("Anticipation", "Monitoring", "Response", "Learning")
)

mean_behaviors$event_type_label <- factor(
  mean_behaviors$event_type_label,
  levels = c("Visit Observation", "Parent/Guardian Interview", "Clinician Interview")
)

# Create the grouped bar plot WITHOUT error bars
p_grouped_no_error <- ggplot(mean_behaviors, 
                             aes(x = resilient_type_label, 
                                 y = mean_behaviors, 
                                 fill = event_type_label)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7, color = "black") +
  scale_fill_manual(values = event_type_grays) +
  labs(
    x = NULL,
    y = "Mean Unique Resilient Behaviors per Patient",
    fill = NULL,
    title = "Mean Unique Resilient Behaviors by Type and Event Source"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 10),
    axis.title.y = element_text(size = 11),
    legend.text = element_text(size = 10),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_y_continuous(limits = c(0, 2.0), breaks = seq(0, 2.0, 0.2))

save_plot(p_grouped_no_error, "mean-behaviors-no-error")
p_grouped_no_error
```

#### Version 2: With 95% Confidence Intervals

**Note:** Error bars are only shown where there is variance in the data. Some combinations have no error bars because all patients had identical numbers of behaviors (zero variance):
- Learning + Visit Observation (all patients had exactly 1 behavior)
- Learning + Parent/Guardian Interview (all patients had exactly 1 behavior)
- Monitoring + Visit Observation (all patients had exactly 1 behavior)

```{r}
#| label: mean-behaviors-plot-with-error
#| fig-width: 10
#| fig-height: 6

# Fix negative CI bounds by setting them to 0
mean_behaviors_adjusted <- mean_behaviors %>%
  mutate(
    ci_lower_adj = pmax(ci_lower, 0)  # Set negative values to 0
  )

# Separate data for error bars (only where SD > 0 AND CI range exists)
mean_behaviors_with_error <- mean_behaviors_adjusted %>%
  filter(sd_behaviors > 0 & (ci_upper - ci_lower_adj) > 0.001)  # Only show if there's a meaningful CI range

# Create the grouped bar plot WITH error bars
p_grouped_with_error <- ggplot(mean_behaviors_adjusted, 
                               aes(x = resilient_type_label, 
                                   y = mean_behaviors, 
                                   fill = event_type_label)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7, color = "black") +
  geom_errorbar(data = mean_behaviors_with_error,
                aes(ymin = ci_lower_adj, ymax = ci_upper),
                position = position_dodge(width = 0.8),
                width = 0.2,
                color = "black",
                linewidth = 0.5) +
  scale_fill_manual(values = event_type_grays) +
  labs(
    x = NULL,
    y = "Mean Unique Resilient Behaviors per Patient",
    fill = NULL,
    title = "Mean Unique Resilient Behaviors with 95% CI"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 10),
    axis.title.y = element_text(size = 11),
    legend.text = element_text(size = 10),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_y_continuous(limits = c(0, 2.0), breaks = seq(0, 2.0, 0.2))

save_plot(p_grouped_with_error, "mean-behaviors-with-error")
p_grouped_with_error
```

*Note: Confidence interval lower bounds that would be negative have been recoded to 0, as negative values are not meaningful for count data.*

## Section 3: Mean Unique Resilient Behaviors by Resilience Characteristics

### Figure 2: Resilience Characteristics Analysis

```{r}
#| label: prepare-resilience-data

# Create mappings for resilience characteristics
resilience_labels <- c(
  "rebound" = "Rebound",
  "robust" = "Robustness",
  "grace" = "Graceful extensibility",
  "new" = "New normal"
)

# The resilience characteristics ARE the safety2_code values themselves
safety_data_resilience <- safety_data %>%
  mutate(
    resilience_type = safety2_code,
    resilience_label = resilience_labels[resilience_type],
    event_type_label = event_type_labels[event_type]
  ) %>%
  filter(resilience_type %in% names(resilience_labels),
         event_type %in% names(event_type_labels))

# Get all unique patients for this analysis
all_patients_res <- unique(safety_data_resilience$patient_id)

# Create all possible combinations
all_combinations_res <- expand.grid(
  patient_id = all_patients_res,
  resilience_type = names(resilience_labels),
  event_type = names(event_type_labels),
  stringsAsFactors = FALSE
) %>%
  mutate(
    resilience_label = resilience_labels[resilience_type],
    event_type_label = event_type_labels[event_type]
  )

# Calculate behaviors per patient-combination
behaviors_per_patient_res <- safety_data_resilience %>%
  group_by(patient_id, resilience_type, event_type) %>%
  summarise(
    n_unique_behaviors = n_distinct(event_id),
    .groups = "drop"
  )

# Join with all combinations to ensure zeros for missing combinations
patient_behaviors_complete_res <- all_combinations_res %>%
  left_join(behaviors_per_patient_res, 
            by = c("patient_id", "resilience_type", "event_type")) %>%
  mutate(n_unique_behaviors = coalesce(n_unique_behaviors, 0L))

# Calculate mean unique behaviors per patient for each combination
mean_behaviors_res <- patient_behaviors_complete_res %>%
  group_by(resilience_type, resilience_label, event_type, event_type_label) %>%
  summarise(
    mean_behaviors = mean(n_unique_behaviors),
    sd_behaviors = sd(n_unique_behaviors),
    n = n(),
    se = sd_behaviors / sqrt(n),
    ci_lower = mean_behaviors - 1.96 * se,
    ci_upper = mean_behaviors + 1.96 * se,
    .groups = "drop"
  )

# Display summary table
knitr::kable(
  mean_behaviors_res %>%
    select(resilience_label, event_type_label, mean_behaviors, ci_lower, ci_upper, n) %>%
    rename(
      "Resilience Characteristic" = resilience_label,
      "Event Type" = event_type_label,
      "Mean Behaviors per Patient" = mean_behaviors,
      "95% CI Lower" = ci_lower,
      "95% CI Upper" = ci_upper,
      "N" = n
    ),
  digits = 3,
  caption = "Mean Unique Resilient Behaviors per Patient by Resilience Characteristic and Event Source"
)
```

### Grouped Bar Charts

#### Version 1: Without Error Bars

```{r}
#| label: resilience-behaviors-plot-no-error
#| fig-width: 10
#| fig-height: 6

# Set factor levels for proper ordering
mean_behaviors_res$resilience_label <- factor(
  mean_behaviors_res$resilience_label,
  levels = c("Rebound", "Robustness", "Graceful extensibility", "New normal")
)

mean_behaviors_res$event_type_label <- factor(
  mean_behaviors_res$event_type_label,
  levels = c("Visit Observation", "Parent/Guardian Interview", "Clinician Interview")
)

# Create the grouped bar plot WITHOUT error bars
p_resilience_no_error <- ggplot(mean_behaviors_res, 
                                aes(x = resilience_label, 
                                    y = mean_behaviors, 
                                    fill = event_type_label)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7, color = "black") +
  scale_fill_manual(values = event_type_grays) +
  labs(
    x = NULL,
    y = "Mean Unique Resilient Behaviors per Patient",
    fill = NULL,
    title = "Mean Unique Resilient Behaviors by Resilience Characteristics"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 10),
    axis.title.y = element_text(size = 11),
    legend.text = element_text(size = 10),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_y_continuous(limits = c(0, 1.4), breaks = seq(0, 1.4, 0.2))

save_plot(p_resilience_no_error, "resilience-behaviors-no-error")
p_resilience_no_error
```

#### Version 2: With 95% Confidence Intervals

```{r}
#| label: resilience-behaviors-plot-with-error
#| fig-width: 10
#| fig-height: 6

# Fix negative CI bounds
mean_behaviors_res_adj <- mean_behaviors_res %>%
  mutate(
    ci_lower_adj = pmax(ci_lower, 0)
  )

# Filter for error bars (only where meaningful)
mean_behaviors_res_error <- mean_behaviors_res_adj %>%
  filter(sd_behaviors > 0 & (ci_upper - ci_lower_adj) > 0.001)

# Create the grouped bar plot WITH error bars
p_resilience_with_error <- ggplot(mean_behaviors_res_adj, 
                                  aes(x = resilience_label, 
                                      y = mean_behaviors, 
                                      fill = event_type_label)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7, color = "black") +
  geom_errorbar(data = mean_behaviors_res_error,
                aes(ymin = ci_lower_adj, ymax = ci_upper),
                position = position_dodge(width = 0.8),
                width = 0.2,
                color = "black",
                linewidth = 0.5) +
  scale_fill_manual(values = event_type_grays) +
  labs(
    x = NULL,
    y = "Mean Unique Resilient Behaviors per Patient",
    fill = NULL,
    title = "Mean Unique Resilient Behaviors by Resilience Characteristics with 95% CI"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 10),
    axis.title.y = element_text(size = 11),
    legend.text = element_text(size = 10),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_y_continuous(limits = c(0, 1.4), breaks = seq(0, 1.4, 0.2))

save_plot(p_resilience_with_error, "resilience-behaviors-with-error")
p_resilience_with_error
```

*Note: Confidence interval lower bounds that would be negative have been recoded to 0. Error bars are not shown for combinations where all patients had identical values (zero variance).*

## Section 4: Mean Unique Resilient Behaviors by Site

### Figure 3: Site Comparison Analysis

```{r}
#| label: prepare-site-data

# Create site labels mapping
site_labels <- c(
  "bch" = "Site 1",
  "cc" = "Site 2",
  "chop" = "Site 3"
)

# Filter for relevant resilient behavior types (ant, mon, resp, learn)
safety_data_sites <- safety_data %>%
  mutate(
    resilient_type = sub("_.*$", "", safety2_code),
    resilient_type_label = resilient_type_labels[resilient_type],
    site_label = site_labels[site_id]
  ) %>%
  filter(resilient_type %in% c("ant", "mon", "resp", "learn"),
         site_id %in% names(site_labels))

# Get all unique patients for this analysis
all_patients_sites <- unique(safety_data_sites$patient_id)

# Create all possible combinations
all_combinations_sites <- expand.grid(
  patient_id = all_patients_sites,
  resilient_type = c("ant", "mon", "resp", "learn"),
  site_id = names(site_labels),
  stringsAsFactors = FALSE
) %>%
  mutate(
    resilient_type_label = resilient_type_labels[resilient_type],
    site_label = site_labels[site_id]
  )

# Calculate behaviors per patient-combination
behaviors_per_patient_sites <- safety_data_sites %>%
  group_by(patient_id, resilient_type, site_id) %>%
  summarise(
    n_unique_behaviors = n_distinct(event_id),
    .groups = "drop"
  )

# Join with all combinations to ensure zeros for missing combinations
patient_behaviors_complete_sites <- all_combinations_sites %>%
  left_join(behaviors_per_patient_sites, 
            by = c("patient_id", "resilient_type", "site_id")) %>%
  mutate(n_unique_behaviors = coalesce(n_unique_behaviors, 0L))

# Calculate mean unique behaviors per patient for each combination
mean_behaviors_sites <- patient_behaviors_complete_sites %>%
  group_by(resilient_type, resilient_type_label, site_id, site_label) %>%
  summarise(
    mean_behaviors = mean(n_unique_behaviors),
    sd_behaviors = sd(n_unique_behaviors),
    n = n(),
    se = sd_behaviors / sqrt(n),
    ci_lower = mean_behaviors - 1.96 * se,
    ci_upper = mean_behaviors + 1.96 * se,
    .groups = "drop"
  )

# Display summary table
knitr::kable(
  mean_behaviors_sites %>%
    select(resilient_type_label, site_label, mean_behaviors, ci_lower, ci_upper, n) %>%
    rename(
      "Resilient Behavior Type" = resilient_type_label,
      "Site" = site_label,
      "Mean Behaviors per Patient" = mean_behaviors,
      "95% CI Lower" = ci_lower,
      "95% CI Upper" = ci_upper,
      "N" = n
    ),
  digits = 3,
  caption = "Mean Unique Resilient Behaviors per Patient by Type and Site"
)
```

### Grouped Bar Charts by Site

#### Version 1: Without Error Bars

```{r}
#| label: site-behaviors-plot-no-error
#| fig-width: 10
#| fig-height: 6

# Set factor levels for proper ordering
mean_behaviors_sites$resilient_type_label <- factor(
  mean_behaviors_sites$resilient_type_label,
  levels = c("Anticipation", "Monitoring", "Response", "Learning")
)

mean_behaviors_sites$site_label <- factor(
  mean_behaviors_sites$site_label,
  levels = c("Site 1", "Site 2", "Site 3")
)

# Create the grouped bar plot WITHOUT error bars
p_sites_no_error <- ggplot(mean_behaviors_sites, 
                           aes(x = resilient_type_label, 
                               y = mean_behaviors, 
                               fill = site_label)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  scale_fill_manual(values = site_grays) +
  labs(
    x = NULL,
    y = "Mean Unique Resilient Behaviors per Patient",
    fill = NULL,
    title = "Mean Unique Resilient Behaviors by Type and Site"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 10),
    axis.title.y = element_text(size = 11),
    legend.text = element_text(size = 10),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_y_continuous(limits = c(0, 4.5), breaks = seq(0, 4.5, 0.5))

save_plot(p_sites_no_error, "site-behaviors-no-error")
p_sites_no_error
```

#### Version 2: With 95% Confidence Intervals

```{r}
#| label: site-behaviors-plot-with-error
#| fig-width: 10
#| fig-height: 6

# Fix negative CI bounds
mean_behaviors_sites_adj <- mean_behaviors_sites %>%
  mutate(
    ci_lower_adj = pmax(ci_lower, 0)
  )

# Filter for error bars (only where meaningful)
mean_behaviors_sites_error <- mean_behaviors_sites_adj %>%
  filter(sd_behaviors > 0 & (ci_upper - ci_lower_adj) > 0.001)

# Create the grouped bar plot WITH error bars
p_sites_with_error <- ggplot(mean_behaviors_sites_adj, 
                             aes(x = resilient_type_label, 
                                 y = mean_behaviors, 
                                 fill = site_label)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  geom_errorbar(data = mean_behaviors_sites_error,
                aes(ymin = ci_lower_adj, ymax = ci_upper),
                position = position_dodge(width = 0.8),
                width = 0.2,
                color = "black",
                linewidth = 0.5) +
  scale_fill_manual(values = site_grays) +
  labs(
    x = NULL,
    y = "Mean Unique Resilient Behaviors per Patient",
    fill = NULL,
    title = "Mean Unique Resilient Behaviors by Type and Site with 95% CI"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 10),
    axis.title.y = element_text(size = 11),
    legend.text = element_text(size = 10),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_y_continuous(limits = c(0, 4.5), breaks = seq(0, 4.5, 0.5))

save_plot(p_sites_with_error, "site-behaviors-with-error")
p_sites_with_error
```

*Note: Confidence interval lower bounds that would be negative have been recoded to 0. Error bars are not shown for combinations where all patients had identical values (zero variance).*

## Section 5: Mean Unique Resilience Characteristics by Site

### Figure 4: Resilience Characteristics by Site Analysis

```{r}
#| label: prepare-resilience-site-data

# Filter for resilience characteristics (rebound, robust, grace, new)
safety_data_res_sites <- safety_data %>%
  mutate(
    resilience_type = safety2_code,
    resilience_label = resilience_labels[resilience_type],
    site_label = site_labels[site_id]
  ) %>%
  filter(resilience_type %in% c("rebound", "robust", "grace", "new"),
         site_id %in% names(site_labels))

# Get all unique patients for this analysis
all_patients_res_sites <- unique(safety_data_res_sites$patient_id)

# Create all possible combinations
all_combinations_res_sites <- expand.grid(
  patient_id = all_patients_res_sites,
  resilience_type = c("rebound", "robust", "grace", "new"),
  site_id = names(site_labels),
  stringsAsFactors = FALSE
) %>%
  mutate(
    resilience_label = resilience_labels[resilience_type],
    site_label = site_labels[site_id]
  )

# Calculate behaviors per patient-combination
behaviors_per_patient_res_sites <- safety_data_res_sites %>%
  group_by(patient_id, resilience_type, site_id) %>%
  summarise(
    n_unique_behaviors = n_distinct(event_id),
    .groups = "drop"
  )

# Join with all combinations to ensure zeros for missing combinations
patient_behaviors_complete_res_sites <- all_combinations_res_sites %>%
  left_join(behaviors_per_patient_res_sites, 
            by = c("patient_id", "resilience_type", "site_id")) %>%
  mutate(n_unique_behaviors = coalesce(n_unique_behaviors, 0L))

# Calculate mean unique behaviors per patient for each combination
mean_behaviors_res_sites <- patient_behaviors_complete_res_sites %>%
  group_by(resilience_type, resilience_label, site_id, site_label) %>%
  summarise(
    mean_behaviors = mean(n_unique_behaviors),
    sd_behaviors = sd(n_unique_behaviors),
    n = n(),
    se = sd_behaviors / sqrt(n),
    ci_lower = mean_behaviors - 1.96 * se,
    ci_upper = mean_behaviors + 1.96 * se,
    .groups = "drop"
  )

# Display summary table
knitr::kable(
  mean_behaviors_res_sites %>%
    select(resilience_label, site_label, mean_behaviors, ci_lower, ci_upper, n) %>%
    rename(
      "Resilience Characteristic" = resilience_label,
      "Site" = site_label,
      "Mean Behaviors per Patient" = mean_behaviors,
      "95% CI Lower" = ci_lower,
      "95% CI Upper" = ci_upper,
      "N" = n
    ),
  digits = 3,
  caption = "Mean Unique Resilience Characteristics per Patient by Site"
)
```

### Grouped Bar Charts by Site

#### Version 1: Without Error Bars

```{r}
#| label: resilience-site-behaviors-plot-no-error
#| fig-width: 10
#| fig-height: 6

# Set factor levels for proper ordering
mean_behaviors_res_sites$resilience_label <- factor(
  mean_behaviors_res_sites$resilience_label,
  levels = c("Rebound", "Robustness", "Graceful extensibility", "New normal")
)

mean_behaviors_res_sites$site_label <- factor(
  mean_behaviors_res_sites$site_label,
  levels = c("Site 1", "Site 2", "Site 3")
)

# Create the grouped bar plot WITHOUT error bars
p_res_sites_no_error <- ggplot(mean_behaviors_res_sites, 
                               aes(x = resilience_label, 
                                   y = mean_behaviors, 
                                   fill = site_label)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  scale_fill_manual(values = site_grays) +
  labs(
    x = NULL,
    y = "Mean Unique Resilient Behaviors per Patient",
    fill = NULL,
    title = "Mean Unique Resilience Characteristics by Site"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 10),
    axis.title.y = element_text(size = 11),
    legend.text = element_text(size = 10),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_y_continuous(limits = c(0, 3.5), breaks = seq(0, 3.5, 0.5))

save_plot(p_res_sites_no_error, "resilience-site-behaviors-no-error")
p_res_sites_no_error
```

#### Version 2: With 95% Confidence Intervals

```{r}
#| label: resilience-site-behaviors-plot-with-error
#| fig-width: 10
#| fig-height: 6

# Fix negative CI bounds
mean_behaviors_res_sites_adj <- mean_behaviors_res_sites %>%
  mutate(
    ci_lower_adj = pmax(ci_lower, 0)
  )

# Filter for error bars (only where meaningful)
mean_behaviors_res_sites_error <- mean_behaviors_res_sites_adj %>%
  filter(sd_behaviors > 0 & (ci_upper - ci_lower_adj) > 0.001)

# Create the grouped bar plot WITH error bars
p_res_sites_with_error <- ggplot(mean_behaviors_res_sites_adj, 
                                 aes(x = resilience_label, 
                                     y = mean_behaviors, 
                                     fill = site_label)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  geom_errorbar(data = mean_behaviors_res_sites_error,
                aes(ymin = ci_lower_adj, ymax = ci_upper),
                position = position_dodge(width = 0.8),
                width = 0.2,
                color = "black",
                linewidth = 0.5) +
  scale_fill_manual(values = site_grays) +
  labs(
    x = NULL,
    y = "Mean Unique Resilient Behaviors per Patient",
    fill = NULL,
    title = "Mean Unique Resilience Characteristics by Site with 95% CI"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 10),
    axis.title.y = element_text(size = 11),
    legend.text = element_text(size = 10),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_y_continuous(limits = c(0, 3.5), breaks = seq(0, 3.5, 0.5))

save_plot(p_res_sites_with_error, "resilience-site-behaviors-with-error")
p_res_sites_with_error
```

*Note: Confidence interval lower bounds that would be negative have been recoded to 0. Error bars are not shown for combinations where all patients had identical values (zero variance).*
